---
title: "NORC_birthdayCard_11302023"
author: "JingWU"
date: "2023-11-30"
output: html_document
# output:
#   pdf_document:
#     extra_dependencies:
#     - float
#     toc: yes
#     toc_depth: 2
#     keep_tex: yes
#     fig_width: 10
#     fig_height: 7
#     fig_caption: yes
#     latex_engine: xelatex
#     df_print: paged

header-includes: \usepackage[labelformat=empty]{caption}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(bigrquery)
library(data.table) ###to write or read and data management 
library(boxr) ###read or write data from/to box
library(tidyverse) ###for data management https://tidyselect.r-lib.org/reference/faq-external-vector.html
#library(dplyr) ###data management
library(reshape)  ###to work on transition from long to wide or wide to long data
library(listr) ###to work on a list of vector, files or..
#library(stringr) ###to work on patterns, charaters
library(plyr)
library(tidyr)
library(tinytex) #for pdf
library(rmarkdown) ###for the output tables into other files: pdf, rtf, etc.
library(janitor) #to get the summary sum
library(finalfit) #https://cran.r-project.org/web/packages/finalfit/vignettes/export.html
library(expss) ###to add labels
library(epiDisplay) ##recommended applied here crosstable, tab1
#library(summarytools) ##recommended not applied in this R code
library(gmodels) ##recommended but not applied in this R code
library(magrittr)
library(arsenal)
library(gtsummary)
library(kableExtra)
#library(patchwork)
library(rio)
library(scales)
```

## R Markdown

NORC will be sending birthday cards via snail mail on a monthly basis to our participants in their birth month.

They will pull the information via API for all participants who are verified and not withdrawn and have birthdays in a given month.

The variables they will need are:

Connect ID
Name (current first and last name from User Profile)
Mailing address (current address from User Profile)
Do not include the date of birth because we do not want to proliferate PII into their system. NORC will make the API call once a month, and we need to populate the list with people whose birthday is that month.

Excluding those deceased (2 participants deceased till now in the participants table 11/30/2023)

```{r, include=FALSE,eval=TRUE,echo=FALSE}
options(knitr.table.format = "latex")
currentDate <- Sys.Date()

#dictionary <- rio::import("https://github.com/episphere/conceptGithubActions/blob/master/aggregate.json",format = "json")
dictionary <- rio::import("https://episphere.github.io/conceptGithubActions/aggregateCopy.json",format = "json")
dd <- dplyr::bind_rows(dictionary,.id="CID")
#dd <- dd[!duplicated(dd),] #remove 140duplicates
#THIS TABLE HAS REPLICATED (CIDS+LABELS) WITH DIFFERENT VARIABLE NAMES,
dd$`Variable Label` <- ifelse(is.na(dd$`Variable Label`), dd$`Variable Name`, dd$`Variable Label`)
#dd <- as.data.frame.matrix(do.call("rbind",dictionary)) #3523, some CID and labels are linked to different variable names 

#dd1 <- dd[!duplicated(dd[,c("CID","Variable Label")]),]
length(unique(dd$CID))
#dd1 <- dd[!duplicated(dd[,c("CID","Variable Label")]),]
length(unique(dd$CID))

#the master dd with more info. on the formats (levels)
urlfile<- "https://raw.githubusercontent.com/episphere/conceptGithubActions/master/csv/masterFile.csv" ###to grab the updated dd from github
y <- read.csv(urlfile)
#dd$labels.combo <- paste(dd$`Variable Label`,dd$`Variable Name`,sep="$")
 bq_auth()
#The bigrquery package is requesting access to your Google account.
#Select a pre-authorised account or enter '0' to obtain a new token.
#Press Esc/Ctrl + C to cancel.

  2 
  
  project <- "nih-nci-dceg-connect-prod-6d04"
  billing <- "nih-nci-dceg-connect-prod-6d04" ##project and billing should be consistent

recr_var <- bq_project_query(project, query="SELECT * FROM  `nih-nci-dceg-connect-prod-6d04.FlatConnect`.INFORMATION_SCHEMA.COLUMN_FIELD_PATHS WHERE table_name='participants_JP'")
recrvar <- bigrquery::bq_table_download(recr_var,bigint = "integer64")
recrvar_d <- recrvar[grepl("d_|D_",recrvar$column_name),]
recrvar$last.CID <- ifelse(grepl("D_", recrvar$field_path), substring(sapply(strsplit(recrvar$field_path,"D_"),tail,1),1,9),
                            ifelse(grepl("d_", recrvar$field_path), substring(sapply(strsplit(recrvar$field_path,"d_"),tail,1),1,9), NA))


pii_cid <- y$conceptId.3[which(y$PII == "Yes")]
recrvar_pii <- recrvar$column_name[which(recrvar$last.CID %in% pii_cid)]

birthcontact <- y[(grepl("399159511|996038075|564964481|521824358|442166669|703385619|634434746|892050548|857217152", y$conceptId.3) | grepl("Verification Variable",y$Current.Question.Text)),]
birth.vars <- recrvar[grepl(paste(birthcontact$conceptId.3,collapse = "|"), recrvar$column_name),]

select <- paste(birth.vars$column_name,collapse=", ")
query <- bq_project_query(project, query=paste("SELECT Connect_Id, token, d_827220437, ", select, " FROM  `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` 
WHERE d_821247024 = '197316935' and d_747006172 != '353358909' and d_987563196!= '353358909'",sep=""))

birth <- bq_table_download(query, bigint="integer64",n_max = Inf, page_size = 5000)

empty_columns <- colSums(is.na(birth) |birth == "") == nrow(birth)
names(birth[,empty_columns])
#[1] "d_569151507_d_399159511" "d_569151507_d_442166669" "d_569151507_d_634434746"
#[4] "d_569151507_d_703385619" "d_569151507_d_892050548" "d_569151507_d_996038075"
birth1 <- birth[!empty_columns]
month <- as.numeric(sapply(strsplit(as.character(currentDate),"-"),"[")[2])

birth1 <- birth1 %>% 
  mutate(Site = case_when(d_827220437 == "531629870" ~"HealthPartners",
                         d_827220437 == '548392715' ~ "Henry Ford Health System", 
                         d_827220437 == '125001209' ~ "Kaiser Permanente Colorado", 
                         d_827220437 == '327912200' ~ "Kaiser Permanente Georgia",
                         d_827220437 == '300267574' ~ "Kaiser Permanente Hawaii",
                         d_827220437 == '452412599' ~ "Kaiser Permanente Northwest", 
                         d_827220437 == '303349821' ~ "Marshfield Clinic Health System",
                         d_827220437 == '657167265' ~ "Sanford Health" , 
                         d_827220437 == '809703864' ~ "University of Chicago Medicine" , 
                         d_827220437  %in% c('517700004','13') ~ "National Cancer Institute",
                         d_827220437 == '181769837' ~ "Other" ),
         NORC = ifelse(d_827220437 =='809703864',"University of Chicago Medicine","NORC"))
#RcrtSI_SignedIn_v1r0 RcrtCS_Consented_v1r0 RcrtUP_Submitted_v1r0  Rcrt_completion_v1r0 Rcrt_Verified_v1r

birth1$Site <- factor(birth1$Site,exclude=NULL,
                    levels=c("HealthPartners", "Henry Ford Health System","Marshfield Clinic Health System",
                             "Sanford Health", "University of Chicago Medicine","Kaiser Permanente Colorado",
                             "Kaiser Permanente Georgia","Kaiser Permanente Hawaii","Kaiser Permanente Northwest",
                             "National Cancer Institute","Other"))


birth2 <- birth1 %>% mutate(`Last Name` = d_996038075,
                            'First Name' = d_399159511,
                            `DOB Month`= d_564964481, 
                            `Address Line 1` = d_521824358,
                            `Address Line 2` = d_442166669,
                            `City`= d_703385619,
                            `State`=d_634434746,
                            `Zip` = d_892050548,
                            'First Name Match'=state_d_147176963,
                            `Last Name Match`=state_d_557461333,
                            `Zip Match`=state_d_559534463,
                            `Token Match`= state_d_679832994,
                            `PIN Match`= state_d_711794630,
                            `DOB Match`= state_d_725929722,
                            preparation_month = ifelse(d_564964481 == "01", 12, as.numeric(d_564964481)-1))
birthday_card <- filter(birth2,!grepl("Chicago",Site) & preparation_month==month) %>%  select(Connect_Id,"Last Name","First Name","Address Line 1",`Address Line 2`,`City`,`State`,`Zip`) 

table(birth2$Site,birth2$d_564964481)

write.csv("NORC_BirthdayCard_",currentDate,".csv")

#Month = sapply(strsplit(format(Sys.Date()1, "%Y %B %b %m"), " "),"[")[2]
Month = sapply(strsplit(format(ymd(Sys.Date()) %m+% months(1), "%Y %B %b %m"), " "),"[")[2] # one month earlier in preparation of the list
box_auth(client_id = "627lww8un9twnoa8f9rjvldf7kb56q1m",
         client_secret = "gSKdYKLd65aQpZGrq9x4QVUNnn5C8qqm") 
box_setwd(dir_id = 237829489634) 

## the box foler Madhuri assigned in dev: https://gcc02.safelinks.protection.outlook.com/?url=https%3A%2F%2Fnih.app.box.com%2Ffolder%2F237829489634%3Ftc%3Dcollab-folder-invite-treatment-b&data=05%7C01%7Cjing.wu2%40nih.gov%7C5b48809fed5849ea8e5808dbf2a4cab1%7C14b77578977342d58507251ca2dc2b06%7C0%7C0%7C638370561812949029%7CUnknown%7CTWFpbGZsb3d8eyJWIjoiMC4wLjAwMDAiLCJQIjoiV2luMzIiLCJBTiI6Ik1haWwiLCJXVCI6Mn0%3D%7C3000%7C%7C%7C&sdata=TLamALLrfxBl8x8NxGH4YLmcoph%2Bx5ryun178wurQd8%3D&reserved=0
box_write(object =birthday_card,file_name=paste("~/Documents/Connect_projects/Biospecimen_Feb2022/Jing_projects/biospecQC_03082022/data/CSV file for ",Month," Birthday Card Recipients_2024.csv",sep=""),na="")


write.table("SELECT Connect_ID, token, d_564964481, d_996038075,d_399159511, d_521824358,d_442166669,d_703385619,d_635101039,d_892050548 FROM  `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` WHERE d_821247024 = '197316935' and d_564964481 = cast(EXTRACT(month FROM current_date()) as string) and d_747006172 != '353358909' and d_987563196 != '353358909' and d_827220437 !=  '809703864'","~/Documents/Connect_projects/Biospecimen_Feb2022/Jing_projects/biospecQC_03082022/data/BirthdayCard_query_11302023.txt", sep="\t",row.names = F,quote = F,col.names = F)

write.table("SELECT Connect_ID, token, d_564964481, d_996038075,d_399159511, d_521824358,d_442166669,d_703385619,d_635101039,d_892050548 FROM  `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` WHERE d_821247024 = '197316935' and cast(d_564964481 as int64) = EXTRACT(month FROM date_add(date_trunc(current_date(),month),interval+1 month)) and d_747006172 != '353358909' and d_987563196 != '353358909' and d_827220437 !=  '809703864'","~/Documents/Connect_projects/Biospecimen_Feb2022/Jing_projects/biospecQC_03082022/data/BirthdayCard_query_11302023.txt", sep="\t",row.names = F,quote = F,col.names = F)
```



```{r pressure, echo=FALSE}

```
