---
title: "Hemolysis_analysis_02052024"
author: "Jing Wu"
execute:
  echo: false
format: 
  html:
      toc: true
      html-math-method: katex
      css: styles.css
editor: visual
---

## Hemolysis - **HP Streck tube pilot analysis**

The hemolysis data: <https://nih.app.box.com/file/1408576499417>. <https://nih.app.box.com/file/1419688124454>

the analytical file: <https://nih.app.box.com/file/1436286215524?s=4gw0cyh0cun4v353k0yw1s5745vz9kod>

 Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
#| echo: false
#| include: false
#| eval: true
#| 
# [hide] 
#| code-fold: true
#| code-summary: "Show the code"

knitr::opts_chunk$set(echo = TRUE)
library(data.table) ###to write or read and data management 
library(bigrquery)
library(boxr) ###read or write data from/to box
library(tidyverse) ###for data management https://tidyselect.r-lib.org/reference/faq-external-vector.html
library(dplyr) ###data management some functions are not available in the dplyr masked in the tidyverse
library(reshape)  ###to work on transition from long to wide or wide to long data
library(listr) ###to work on a list of vector, files or..
#library(sqldf) ##sql
#library(lubridate) ###date time it is already masked in 'tidyverse'
library(ggplot2) ###plots
library(ggpubr) ###for the publications of plots
library(RColorBrewer) ###visions color http://www.sthda.com/english/wiki/colors-in-r
library(gridExtra)
#library(stringr) ###to work on patterns, charaters
library(plyr)
library(tidyr)
library(tinytex) #for pdf
library(rmarkdown) ###for the output tables into other files: pdf, rtf, etc.
library(janitor) #to get the summary sum
library(finalfit) #https://cran.r-project.org/web/packages/finalfit/vignettes/export.html t
library(expss) ###to add labels
library(epiDisplay) ##recommended applied here crosstable, tab1
#library(summarytools) ##recommended not applied in this R code
library(gmodels) ##recommended but not applied in this R code
library(magrittr)
library(arsenal)
library(gtsummary)
library(kableExtra)
#library(patchwork)
library(rio)
library(readxl)
library(purrr)
library(lme4)
library(skimr)

box_auth(client_id = "627lww8un9twnoa8f9rjvldf7kb56q1m",
         client_secret = "gSKdYKLd65aQpZGrq9x4QVUNnn5C8qqm")
```

Import the working data from Box: /Users/wuj12/Library/CloudStorage/Box-Box/CONNECT_DCEG ONLY/Biospecimen_DCEG ONLY/STRECK Tube (<https://nih.app.box.com/folder/229338866264?s=n3hxbtbmaze5f1sv8kpk63rufmgrn0f3>)

<https://nih.app.box.com/folder/244206033569>

```{r}
#| code-fold: true
#| code-summary: "Show the code"

#| echo: false
#| include: false
#| eval: true
# [hide] 
box_setwd(dir_id =244206033569)
hemolysis <- box_read(file_id=1419688124454)
# Remote file '/var/folders/z2/6938nzld299b956wrk2w0s8nw8s4d2/T//RtmplC5IRS/MERGED_ShipComTemps_BSI_HP STRECK Pilot.xlsx' read into memory as an object of class data.frame
table(hemolysis$Hemolyzed, hemolysis$`Material Type`)
                   
  #                  PLASMA SERUM WHOLE BL
  # not hem (1)          247   762        0
  # slight hemo (2-3)    269     0        0
  # mod hem(4-5)          48     0        0
  # severe hemo (6-7)     39     0        0

length(unique(hemolysis$Connect_ID))
# [1] 410

names(hemolysis)
#  [1] "RcrtES_Site_v1r0"                   "BioSpm_Setting_v1r0"               
#  [3] "Connect_ID"                         "BioSpm_ColIDScan_v1r0"             
#  [5] "BioCol_ColTime_v1r0"                "BioClin_ClinBloodTmBL_v1r0"        
#  [7] "BioClin_ClinicalUrnTmBL_v1r0"       "BioPack_BoxID_v1r0"                
#  [9] "BioBPTL_ShipComments_v1r0"          "BSI ID"                            
# [11] "Sequence"                           "Date Drawn"                        
# [13] "Date Received"                      "Date Processed"                    
# [15] "Material Type"                      "Additive/Preservative"             
# [17] "Hemolyzed"                          "Specimen Character"                
# [19] "Box Comments"                       "Box Temperature on arrival"        
# [21] "BioCol_PhlebInitials_v1r0"          "Box Lowest Temp during Transit"    
# [23] "If frozen, How long frozen (hours)"
 table(hemolysis$Hemolyzed)
     # mod hem(4-5)       not hem (1) severe hemo (6-7) slight hemo (2-3) 
     #           30              1003                39               253 
 hemolysis <- hemolysis %>% 
   mutate(anticoagulant = ifelse(grepl("EDTA", `Additive/Preservative`),  "EDTA = K2",  `Additive/Preservative`),
          hemo_class = case_when(Hemolyzed %in% c("mod hem(4-5)", "severe hemo (6-7)") ~ 2,
                                Hemolyzed == "slight hemo (2-3)" ~ 1,
                                Hemolyzed =="not hem (1)" ~0),
          hemo_flag = case_when(Hemolyzed %in% c("mod hem(4-5)", "severe hemo (6-7)", "slight hemo (2-3)") ~ 1,
                                 Hemolyzed =="not hem (1)" ~0),
          Hemolyzed = factor(Hemolyzed, levels= c("not hem (1)","slight hemo (2-3)","mod hem(4-5)", "severe hemo (6-7)" )),
          hemo_severe = case_when(Hemolyzed %in% c("mod hem(4-5)", "severe hemo (6-7)") ~ 1,
                                Hemolyzed %in% c("not hem (1)", "slight hemo (2-3)") ~0),
          Temperature_changes_C=ifelse(BioBPTL_ShipComments_v1r0 !=" " & `Box Lowest Temp during Transit` !=" ", as.numeric(gsub("C|c","",str_split_i(BioBPTL_ShipComments_v1r0," ",-1)))- as.numeric(gsub("C|c","",`Box Lowest Temp during Transit`)), NA),
          Box_Temperature_arrival = as.numeric(gsub("C|c","",`Box Temperature on arrival`)),
          Box_Teperature_Lowest_transit = as.numeric(gsub("C|c","",`Box Lowest Temp during Transit`)),
          days_received_drawn = difftime(as_date(`Date Received`), as_date(`Date Drawn`),units="days"),
          Phlebotomist = toupper(BioCol_PhlebInitials_v1r0),
          Specimen_Character=ifelse(is.na(`Specimen Character`), "not mentioned",`Specimen Character`),
          lipedimia = ifelse(is.na(`Specimen Character`), 0, ifelse(grepl("Lipemic", `Specimen Character`), 1, 0 ))) #563
 
 hemolysis$days_drawn_processed =difftime(hemolysis$"Date Processed", hemolysis$"Date Drawn",units="days") 
 
 breaks <- hour(hm("00:00", "6:00", "12:00", "18:00", "23:59"))
# labels for the breaks
labels <- c("Night", "Morning", "Afternoon", "Evening")

hemolysis$Time_of_day <- cut(x=hour(hemolysis$"Date Drawn"), breaks = breaks, labels = labels, include.lowest=TRUE)

 
 hemolysis <- hemolysis %>%
   mutate(days_drawn_process_cat = case_when(as.numeric(days_drawn_processed) <= 1 ~ "1 or less than 1 days",
                                             as.numeric(days_drawn_processed) >1 &as.numeric(days_drawn_processed) <= 2 ~ "1 + or <2 days",
                                             as.numeric(days_drawn_processed) >2 & as.numeric(days_drawn_processed) <=3 ~ " 2+ or 3 days",
                                             as.numeric(days_drawn_processed) > 3 & as.numeric(days_drawn_processed) <=5 ~ "4-5 days",
                                             as.numeric(days_drawn_processed) > 5 & as.numeric(days_drawn_processed) <=10 ~ ">5-10 days",
                                             as.numeric(days_drawn_processed) > 10 & as.numeric(days_drawn_processed) <=15 ~ ">10-15 days",
                                             as.numeric(days_drawn_processed) > 15 & as.numeric(days_drawn_processed) <=30 ~ ">15-30 days",
                                             as.numeric(days_drawn_processed) > 30  ~ "30 days more"),
           Phlebotomist = ifelse(toupper(BioCol_PhlebInitials_v1r0) %in% c("CG","CSG"),"CG/CSG", ifelse(toupper(BioCol_PhlebInitials_v1r0) %in% c("OJ","OJS","OS"), "OJ/OJS/OS",toupper(BioCol_PhlebInitials_v1r0) ))) 
 
 hemo_plasma <- filter(hemolysis, `Material Type` == "PLASMA") %>% 
   mutate(hemo_class = case_when(Hemolyzed %in% c("mod hem(4-5)", "severe hemo (6-7)") ~ 2,
                                Hemolyzed == "slight hemo (2-3)" ~ 1,
                                Hemolyzed =="not hem (1)" ~0),
          hemo_flag = case_when(Hemolyzed %in% c("mod hem(4-5)", "severe hemo (6-7)", "slight hemo (2-3)") ~ 1,
                                 Hemolyzed =="not hem (1)" ~0),
          Hemolyzed = factor(Hemolyzed, levels= c("not hem (1)","slight hemo (2-3)","mod hem(4-5)", "severe hemo (6-7)" )),
          hemo_severe = case_when(Hemolyzed %in% c("mod hem(4-5)", "severe hemo (6-7)") ~ 1,
                                Hemolyzed %in% c("not hem (1)", "slight hemo (2-3)") ~0),
          Temperature_changes_C=as.numeric(gsub("C|c","",str_split_i(BioBPTL_ShipComments_v1r0," ",-1)))- as.numeric(gsub("C|c","",`Box Lowest Temp during Transit`)),
          Box_Temperature_arrival = as.numeric(gsub("C|c","",`Box Temperature on arrival`)),
          Box_Teperature_Lowest_transit = as.numeric(gsub("C|c","",`Box Lowest Temp during Transit`)),
         days_received_drawn = difftime(as_date(`Date Received`), as_date(`Date Drawn`),units="days"),
         Phlebotomist = toupper(BioCol_PhlebInitials_v1r0))#563
 
 hemo_plasma$days_drawn_processed =difftime(hemo_plasma$"Date Processed", hemo_plasma$"Date Drawn",units="days")  
          
collectID.nodup <- unique(hemo_plasma$BioSpm_ColIDScan_v1r0...6[duplicated(hemo_plasma$BioSpm_ColIDScan_v1r0...6)]) #Connect_ID 2333088669


hemo_settings <- hemo_plasma %>% 
  select(hemo_class,BioSpm_Setting_v1r0) %>%
  tbl_cross(col = hemo_class,
            row = BioSpm_Setting_v1r0,
            label = list(hemo_class~"mod or severe hemolysis",
                         BioSpm_Setting_v1r0 ~"Research/Clinical Settings" ),
            digits=c(0,2),
            percent = c("col"),
            missing = "ifany",
            margin_text = "Total Plasma",
            missing_text = "(Missing)") %>%
            bold_labels() %>%
           #italicize_levels() %>% 
           modify_header() 

hemo_clotting <- hemo_plasma %>% 
  select(Hemolyzed,`Additive/Preservative`) %>%
  tbl_cross(col = Hemolyzed,
            row = `Additive/Preservative`,
            label = list(Hemolyzed~"Completion of Baseline Surveys",
                         `Additive/Preservative` ~"clotting agent" ),
            digits=c(0,2),
            percent = c("cell"),
            missing = "ifany",
            margin_text = "Total Verified Participants",
            missing_text = "(Missing)") %>%
            bold_labels() %>%
           #italicize_levels() %>% 
           modify_header() 

hemo_phlebotomist <- hemo_plasma %>% 
  select(hemo_flag,Phlebotomist) %>%
  tbl_cross(col = hemo_flag,
            row = Phlebotomist,
            label = list(hemo_flag~"Any hemolysis",
                         Phlebotomist ~"Phlebotomist" ),
            digits=c(0,2),
            percent = c("col"),
            missing = "ifany",
            margin_text = "Total Plasma",
            missing_text = "(Missing)") %>%
            bold_labels() %>%
           #italicize_levels() %>% 
           modify_header() 

hemo_phlebotomist1 <- hemo_plasma %>% 
  select(hemo_class,Phlebotomist) %>%
  tbl_cross(col = hemo_class,
            row = Phlebotomist,
            label = list(hemo_class~"mod or severe hemolysis",
                         Phlebotomist ~"Phlebotomist" ),
            digits=c(0,2),
            percent = c("col"),
            missing = "ifany",
            margin_text = "Total Plasma",
            missing_text = "(Missing)") %>%
            bold_labels() %>%
           #italicize_levels() %>% 
           modify_header() 

hemo_NeedleRecpt <- hemo_plasma %>% 
  select(hemo_class,days_received_drawn) %>%
  tbl_cross(col = hemo_class,
            row = days_received_drawn,
            label = list(hemo_class~"mod or severe hemolysis",
                         days_received_drawn ~"Days from Blood Drawn to Received" ),
            digits=c(0,2),
            percent = c("col"),
            missing = "ifany",
            margin_text = "Total Plasma",
            missing_text = "(Missing)") %>%
            bold_labels() %>%
           #italicize_levels() %>% 
           modify_header() 

```

The general info. of hemolysis data and the hemolyzed blood collections;

```{r}
#| code-fold: true
#| code-summary: "Show the code"

#| echo: false
#| include: false
#| eval: true
#| 
# [hide] 
hemo_all <- hemolysis %>% dplyr::select(Hemolyzed,RcrtES_Site_v1r0,BioSpm_Setting_v1r0,Sequence,anticoagulant,Phlebotomist,`Specimen Character`,`Material Type`,hemo_flag,hemo_severe,
                                        days_drawn_processed,days_received_drawn, Box_Temperature_arrival,Temperature_changes_C,Box_Teperature_Lowest_transit) %>% mutate(Sequence = as.factor(Sequence),
Hemolyzed =  ifelse(is.na(Hemolyzed),"Missing", Hemolyzed),
days_received_drawn = as.numeric(days_received_drawn),
Box_Temperature_arrival = as.numeric(Box_Temperature_arrival),
Temperature_changes_C =as.numeric(Temperature_changes_C),
Box_Teperature_Lowest_transit = as.numeric(Box_Teperature_Lowest_transit)) %>% as_tibble() %>%
    tbl_summary(by = Hemolyzed,
                type   = all_categorical() ~ "categorical", 
                
                statistic = list(all_continuous() ~ "{median} ({p25}, {p75})",
                                 all_categorical() ~ "{n} / {N} ({p}%)"),
                
                missing_text = 'missing',
                digits = all_continuous() ~ 2) %>%
    #add_p(pvalue_fun = ~ style_pvalue(.x, digits = 2)) %>%
    add_overall() %>%
    add_n() %>%
    modify_header(label ~ "**Variable**") %>%
    modify_spanning_header(c("stat_1", "stat_2","stat_3", "stat_4") ~ "**Hemolyzed Status**") %>%
    modify_footnote(
        all_stat_cols() ~ "Median (IQR) or Frequency (%)"
    ) %>%
    modify_caption("**Table 1. All Blood Collection Characteristics**") %>%
    bold_labels() %>% 
    as_kable_extra(escape = FALSE, addtl_fmt = TRUE)

hemo_summ <- hemo_plasma %>% dplyr::select(Hemolyzed,BioSpm_Setting_v1r0,Sequence,`Additive/Preservative`,`Specimen Character`,Phlebotomist,hemo_flag,hemo_severe,days_drawn_processed,days_received_drawn,Box_Temperature_arrival,Temperature_changes_C,Box_Teperature_Lowest_transit) %>% mutate(Sequence = as.factor(Sequence)) %>% as_tibble() %>%
    tbl_summary(by = Hemolyzed,
                statistic = list(all_continuous() ~ "{mean} ({sd})",
                                 all_categorical() ~ "{n} / {N} ({p}%)"),
                
                digits = all_continuous() ~ 2) %>%
    #add_p(pvalue_fun = ~ style_pvalue(.x, digits = 2)) %>%
    add_overall() %>%
    add_n() %>%
    modify_header(label ~ "**Variable**") %>%
    #modify_spanning_header(c("stat_1", "stat_2") ~ "**Hemolyzed Status**") %>%
    modify_footnote(
        all_stat_cols() ~ "Median (IQR) or Frequency (%)"
    ) %>%
    modify_caption("**Table 1. Blood Plasma Collection Characteristics**") %>%
    bold_labels() %>%
    as_kable_extra(escape = FALSE, addtl_fmt = TRUE)
```

```{r}
#| code-fold: true
#| code-summary: "Show the code"

#| echo: false
#| eval: true
#| output: true
# [hide]  
options(knitr.table.format = "latex")
options(kableExtra.auto_format = FALSE)

hemo_all
hemo_summ
print(summary(glmer( hemo_flag ~ as.numeric(days_drawn_processed) + Box_Temperature_arrival+ Box_Teperature_Lowest_transit+ as.factor(hemo_plasma$BioPack_BoxID_v1r0) +  `Additive/Preservative` + (1|BioSpm_ColIDScan_v1r0...6), data=hemo_plasma,family="poisson",glmerControl(optimizer = "bobyqa"), nAGQ=10)))

##results on data Feb. 07 2024 the most current data
##fixed-effect model matrix is rank deficient so dropping 1 column / coefficient
# boundary (singular) fit: see help('isSingular')
# Generalized linear mixed model fit by maximum likelihood (Adaptive Gauss-Hermite Quadrature,
#   nAGQ = 10) [glmerMod]
#  Family: poisson  ( log )
# Formula: hemo_class ~ as.numeric(days_drawn_processed) + Box_Temperature_arrival +  
#     Box_Teperature_Lowest_transit + as.factor(hemo_plasma$BioPack_BoxID_v1r0) +  
#     `Additive/Preservative` + (1 | BioSpm_ColIDScan_v1r0...6)
#    Data: hemo_plasma
# Control: glmerControl(optimizer = "bobyqa")
# 
#      AIC      BIC   logLik deviance df.resid 
#    490.6    671.1   -204.3    408.6      562 
# 
# Scaled residuals: 
#      Min       1Q   Median       3Q      Max 
# -1.29131 -0.67173  0.09641  0.40904  2.74274 
# 
# Random effects:
#  Groups                    Name        Variance Std.Dev.
#  BioSpm_ColIDScan_v1r0...6 (Intercept) 0        0       
# Number of obs: 603, groups:  BioSpm_ColIDScan_v1r0...6, 403
# 
# Fixed effects:
#                                                 Estimate Std. Error z value Pr(>|z|)    
# (Intercept)                                      0.66951    1.12264   0.596 0.550926    
# as.numeric(days_drawn_processed)                 0.04127    0.01072   3.848 0.000119 ***
# Box_Temperature_arrival                         -0.13684    0.70270  -0.195 0.845602    
# Box_Teperature_Lowest_transit                   -0.25607    0.95898  -0.267 0.789448    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box691 -1.11710    0.67995  -1.643 0.100400    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box693 -0.31100    1.78476  -0.174 0.861664    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box695 -0.45245    0.87321  -0.518 0.604355    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box697 -0.46710    2.83000  -0.165 0.868902    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box699 -2.47599    1.44087  -1.718 0.085723 .  
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box701 -0.47541    0.31576  -1.506 0.132166    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box702 -0.38860    0.45411  -0.856 0.392142    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box703 -2.20910    2.24047  -0.986 0.324135    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box704 -1.56922    0.89245  -1.758 0.078692 .  
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box705 -1.71790    1.99667  -0.860 0.389576    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box707 -0.53490    0.55349  -0.966 0.333836    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box708 -0.82203    2.52064  -0.326 0.744334    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box709 -0.91605    1.84756  -0.496 0.620024    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box710 -0.12424    1.21757  -0.102 0.918728    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box712 -0.46601    0.52557  -0.887 0.375256    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box713 -0.21605    0.44173  -0.489 0.624769    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box714  0.02235    0.53556   0.042 0.966712    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box715 -0.96551    1.52879  -0.632 0.527680    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box716 -0.88934    1.38198  -0.644 0.519883    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box717 -0.38540    0.53862  -0.716 0.474276    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box718 -0.31969    0.37152  -0.861 0.389510    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box719  0.23421    0.44115   0.531 0.595488    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box720 -0.79815    0.93650  -0.852 0.394064    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box721 -1.32456    2.42397  -0.546 0.584761    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box722 -0.56170    0.48603  -1.156 0.247808    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box723 -1.48154    1.04184  -1.422 0.155014    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box724 -1.32081    0.94427  -1.399 0.161883    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box725 -0.60399    0.49847  -1.212 0.225628    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box727 -0.76577    1.71829  -0.446 0.655843    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box728 -0.66206    0.57602  -1.149 0.250409    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box729 -0.76232    3.23940  -0.235 0.813954    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box731 -0.46582    3.34137  -0.139 0.889125    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box732 -0.07415    0.42095  -0.176 0.860177    
# as.factor(hemo_plasma$BioPack_BoxID_v1r0)Box733 -0.60131    4.90292  -0.123 0.902390  
# `Additive/Preservative`Lithium Heparin           0.29438    0.23622   1.246 0.212694    
# `Additive/Preservative`Streck DNA Stabilizer     0.79956    0.32741   2.442 0.014604 *  
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

print(summary(glmer( hemo_severe ~ as.numeric(days_drawn_processed) +Phlebotomist+ Box_Temperature_arrival+  `Additive/Preservative` + (1|BioPack_BoxID_v1r0), data=hemo_plasma,family="poisson",glmerControl(optimizer = "bobyqa"), nAGQ=10)))
# Generalized linear mixed model fit by maximum likelihood (Adaptive Gauss-Hermite Quadrature, nAGQ = 10) ['glmerMod']
#  Family: poisson  ( log )
# Formula: hemo_severe ~ as.numeric(days_drawn_processed) + Box_Temperature_arrival +  
#     `Additive/Preservative` + (1 | BioPack_BoxID_v1r0)
#    Data: hemo_plasma
# Control: glmerControl(optimizer = "bobyqa")
# 
#      AIC      BIC   logLik deviance df.resid 
#    236.4    262.4   -112.2    224.4      557 
# 
# Scaled residuals: 
#     Min      1Q  Median      3Q     Max 
# -0.9629 -0.2880 -0.2447 -0.1323  4.6325 
# 
# Random effects:
#  Groups             Name        Variance Std.Dev.
#  BioPack_BoxID_v1r0 (Intercept) 0.2246   0.4739  
# Number of obs: 563, groups:  BioPack_BoxID_v1r0, 33
# 
# Fixed effects:
#                                              Estimate Std. Error z value Pr(>|z|)    
# (Intercept)                                  -6.83577    1.61859  -4.223 2.41e-05 ***
# as.numeric(days_drawn_processed)              0.14489    0.03855   3.759 0.000171 ***
# Box_Temperature_arrival                       0.02386    0.13666   0.175 0.861396    
# `Additive/Preservative`Lithium Heparin        0.63802    0.47716   1.337 0.181183    
# `Additive/Preservative`Streck DNA Stabilizer  3.89778    1.42469   2.736 0.006221 ** 
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
# 
# Correlation of Fixed Effects:
#             (Intr) a.(__) Bx_Tm_ `A/P`H
# as.nmrc(__) -0.914                     
# Bx_Tmprtr_r -0.401  0.022              
# `Addtv/P`LH -0.062  0.098 -0.179       
# `Ad/P`SDNAS -0.917  0.979  0.031  0.140

m1<- glmer( hemo_flag ~ as.numeric(days_drawn_processed) + as.factor(lipedimia)+   as.factor(`Additive/Preservative`)  + (1|BioSpm_ColIDScan_v1r0...6), data=hemolysis,family="poisson",glmerControl(optimizer = "bobyqa"), nAGQ=10)

m1_int <- glmer( hemo_flag ~ as.numeric(days_drawn_processed) + as.factor(lipedimia)+   as.factor(`Additive/Preservative`) + as.factor(lipedimia)*as.factor(`Additive/Preservative`) + (1|BioSpm_ColIDScan_v1r0...6), data=hemolysis,family="poisson",glmerControl(optimizer = "bobyqa"), nAGQ=10)
anova(m1_int,m1)
# Data: hemolysis
# Models:
# m1: hemo_flag ~ as.numeric(days_drawn_processed) + as.factor(lipedimia) + as.factor(`Additive/Preservative`) + (1 | BioSpm_ColIDScan_v1r0...6)
# m1_int: hemo_flag ~ as.numeric(days_drawn_processed) + as.factor(lipedimia) + as.factor(`Additive/Preservative`) + as.factor(lipedimia) * as.factor(`Additive/Preservative`) + (1 | BioSpm_ColIDScan_v1r0...6)
#        npar    AIC    BIC  logLik deviance  Chisq Df Pr(>Chisq)
# m1        7 373.37 409.88 -179.68   359.37                     
# m1_int   10 375.99 428.15 -178.00   355.99 3.3739  3     0.3375



summary(glmer( hemo_flag ~ as.numeric(days_drawn_processed) + as.factor(lipedimia)+  as.factor(`Additive/Preservative`)  + (1|BioSpm_ColIDScan_v1r0...6), data=hemolysis,family="poisson",glmerControl(optimizer = "bobyqa"), nAGQ=10))
# boundary (singular) fit: see help('isSingular')
# Generalized linear mixed model fit by maximum likelihood (Adaptive Gauss-Hermite
#   Quadrature, nAGQ = 10) [glmerMod]
#  Family: poisson  ( log )
# Formula: hemo_flag ~ as.numeric(days_drawn_processed) + as.factor(lipedimia) +  
#     as.factor(`Additive/Preservative`) + (1 | BioSpm_ColIDScan_v1r0...6)
#    Data: hemolysis
# Control: glmerControl(optimizer = "bobyqa")
# 
#      AIC      BIC   logLik deviance df.resid 
#    373.4    409.9   -179.7    359.4     1354 
# 
# Scaled residuals: 
#      Min       1Q   Median       3Q      Max 
# -1.01317 -0.00001 -0.00001  0.28530  1.08526 
# 
# Random effects:
#  Groups                    Name        Variance Std.Dev.
#  BioSpm_ColIDScan_v1r0...6 (Intercept) 0        0       
# Number of obs: 1361, groups:  BioSpm_ColIDScan_v1r0...6, 410
# 
# Fixed effects:
#                                                           Estimate Std. Error z value
# (Intercept)                                              -1.173278   0.237911  -4.932
# as.numeric(days_drawn_processed)                          0.019880   0.007102   2.799
# as.factor(lipedimia)1                                     0.343542   0.119038   2.886
# as.factor(`Additive/Preservative`)Lithium Heparin         0.291975   0.262969   1.110
# as.factor(`Additive/Preservative`)SST                   -22.138286 193.517823  -0.114
# as.factor(`Additive/Preservative`)Streck DNA Stabilizer   0.389711   0.238281   1.636
#                                                         Pr(>|z|)    
# (Intercept)                                             8.16e-07 ***
# as.numeric(days_drawn_processed)                         0.00512 ** 
# as.factor(lipedimia)1                                    0.00390 ** 
# as.factor(`Additive/Preservative`)Lithium Heparin        0.26687    
# as.factor(`Additive/Preservative`)SST                    0.90892    
# as.factor(`Additive/Preservative`)Streck DNA Stabilizer  0.10194    
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
# 
# Correlation of Fixed Effects:
#             (Intr) a.(__) as.()1 a.(`AH a.(`A/
# as.nmrc(__) -0.903                            
# as.fctr(l)1 -0.199  0.086                     
# a.(`A/P`)LH -0.241  0.090  0.055              
# a.(`A/P`)SS  0.000  0.000  0.000  0.000       
# a.(`A/P`)DS -0.901  0.840 -0.151  0.218  0.000
# optimizer (bobyqa) convergence code: 0 (OK)
# boundary (singular) fit: see help('isSingular')


summary(glmer( hemo_flag ~ as.numeric(days_drawn_processed) +   as.factor(`Additive/Preservative`)  + (1|BioSpm_ColIDScan_v1r0...6), data=hemolysis,family="poisson",glmerControl(optimizer = "bobyqa"), nAGQ=10))
# boundary (singular) fit: see help('isSingular')
# Generalized linear mixed model fit by maximum likelihood (Adaptive Gauss-Hermite
#   Quadrature, nAGQ = 10) [glmerMod]
#  Family: poisson  ( log )
# Formula: 
# hemo_flag ~ as.numeric(days_drawn_processed) + as.factor(`Additive/Preservative`) +  
#     (1 | BioSpm_ColIDScan_v1r0...6)
#    Data: hemolysis
# Control: glmerControl(optimizer = "bobyqa")
# 
#      AIC      BIC   logLik deviance df.resid 
#    379.8    411.1   -183.9    367.8     1355 
# 
# Scaled residuals: 
#      Min       1Q   Median       3Q      Max 
# -0.98635 -0.00001 -0.00001  0.26798  0.96453 
# 
# Random effects:
#  Groups                    Name        Variance Std.Dev.
#  BioSpm_ColIDScan_v1r0...6 (Intercept) 0        0       
# Number of obs: 1361, groups:  BioSpm_ColIDScan_v1r0...6, 410
# 
# Fixed effects:
#                                                           Estimate Std. Error z value
# (Intercept)                                             -1.050e+00  2.350e-01  -4.469
# as.numeric(days_drawn_processed)                         1.825e-02  7.118e-03   2.564
# as.factor(`Additive/Preservative`)Lithium Heparin        2.532e-01  2.631e-01   0.962
# as.factor(`Additive/Preservative`)SST                   -2.225e+01  4.009e+03  -0.006
# as.factor(`Additive/Preservative`)Streck DNA Stabilizer  4.942e-01  2.373e-01   2.082
#                                                         Pr(>|z|)    
# (Intercept)                                             7.85e-06 ***
# as.numeric(days_drawn_processed)                          0.0103 *  
# as.factor(`Additive/Preservative`)Lithium Heparin         0.3359    
# as.factor(`Additive/Preservative`)SST                     0.9956    
# as.factor(`Additive/Preservative`)Streck DNA Stabilizer   0.0373 *  
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
# 
# Correlation of Fixed Effects:
#             (Intr) a.(__) a.(`AH a.(`A/
# as.nmrc(__) -0.909                     
# a.(`A/P`)LH -0.251  0.105              
# a.(`A/P`)SS  0.000  0.000  0.000       
# a.(`A/P`)DS -0.961  0.868  0.245  0.000
# optimizer (bobyqa) convergence code: 0 (OK)
# boundary (singular) fit: see help('isSingular')
# 
# Warning messages:
# 1: In vcov.merMod(object, use.hessian = use.hessian) :
#   variance-covariance matrix computed from finite-difference Hessian is
# not positive definite or contains NA values: falling back to var-cov estimated from RX
# 2: In vcov.merMod(object, correlation = correlation, sigm = sig) :
#   variance-covariance matrix computed from finite-difference Hessian is
# not positive definite or contains NA values: falling back to var-cov estimated from RX


library(survival)
collectID.nodup <- unique(hemo_plasma$BioSpm_ColIDScan_v1r0...6[duplicated(hemo_plasma$BioSpm_ColIDScan_v1r0...6)])

hemo_plasma.dup <- filter(hemo_plasma, BioSpm_ColIDScan_v1r0...6 %in% collectID.nodup) 

fit.clr <- clogit(hemo_flag ~ days_drawn_processed + `Additive/Preservative`+ strata(BioSpm_ColIDScan_v1r0...6, BioPack_BoxID_v1r0),
                  data = hemo_plasma.dup)
summary(fit.clr)

# Regression coefficient
round(summary(fit.clr)$coef, 4)

fit.clr <- clogit(hemo_flag ~ days_drawn_processed + `Additive/Preservative`+ strata(BioSpm_ColIDScan_v1r0...6, BioPack_BoxID_v1r0),
                  data = hemo_plasma.dup[which(hemo_plasma.dup$`Additive/Preservative`!="Lithium Heparin" ),])
summary(fit.clr)
Call:
coxph(formula = Surv(rep(1, 354L), hemo_flag) ~ days_drawn_processed + 
    `Additive/Preservative` + strata(BioSpm_ColIDScan_v1r0...6, 
    BioPack_BoxID_v1r0), data = hemo_plasma.dup[which(hemo_plasma.dup$`Additive/Preservative` != 
    "Lithium Heparin"), ], method = "exact")

#   n= 353, number of events= 190 
#    (1 observation deleted due to missingness)
# 
#                                                 coef exp(coef) se(coef)     z Pr(>|z|)   
# days_drawn_processed                         0.06319   1.06523  0.01971 3.206  0.00135 **
# `Additive/Preservative`Streck DNA Stabilizer 1.14779   3.15121  0.54949 2.089  0.03672 * 
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
# 
#                                              exp(coef) exp(-coef) lower .95 upper .95
# days_drawn_processed                             1.065     0.9388     1.025     1.107
# `Additive/Preservative`Streck DNA Stabilizer     3.151     0.3173     1.073     9.251
# 
# Concordance= 0.693  (se = 0.075 )
# Likelihood ratio test= 15.37  on 2 df,   p=5e-04
# Wald test            = 12.81  on 2 df,   p=0.002
# Score (logrank) test = 14.5  on 2 df,   p=7e-04


nolip_strk <- filter(hemolysis, is.na(`Specimen Character`)) 


clogit(hemo_flag ~ days_drawn_processed + `Additive/Preservative`+ strata(BioSpm_ColIDScan_v1r0...6, BioPack_BoxID_v1r0),data = hemolysis[which(!is.na(hemolysis$`Specimen Character`) & hemolysis$anticoagulant %in% c("EDTA = K2", "Streck DNA Stabilizer")),])

# Call:
# clogit(hemo_flag ~ days_drawn_processed + `Additive/Preservative` + 
#     strata(BioSpm_ColIDScan_v1r0...6, BioPack_BoxID_v1r0), data = hemolysis[which(!is.na(hemolysis$`Specimen Character`) & 
#     hemolysis$anticoagulant %in% c("EDTA = K2", "Streck DNA Stabilizer")), 
#     ])
# 
#                                                 coef exp(coef) se(coef)     z     p
# days_drawn_processed                         0.05599   1.05759  0.04703 1.191 0.234
# `Additive/Preservative`Streck DNA Stabilizer 0.79421   2.21270  1.03390 0.768 0.442
# 
# Likelihood ratio test=1.87  on 2 df, p=0.3921
# n= 285, number of events= 189 
# there is no significant difference between Streck and EDTA in the relation with hemolysis among those samples with lipedimia

clogit(hemo_flag ~ days_drawn_processed + `Additive/Preservative`+ strata(BioSpm_ColIDScan_v1r0...6, BioPack_BoxID_v1r0), data = hemolysis[which(is.na(hemolysis$`Specimen Character`)&     hemolysis$anticoagulant %in% c("EDTA = K2", "Streck DNA Stabilizer")),])
# Call:
# clogit(hemo_flag ~ days_drawn_processed + `Additive/Preservative` + 
#     strata(BioSpm_ColIDScan_v1r0...6, BioPack_BoxID_v1r0), data = hemolysis[which(is.na(hemolysis$`Specimen Character`) & 
#     hemolysis$anticoagulant %in% c("EDTA = K2", "Streck DNA Stabilizer")), 
#     ])
# 
#                                                  coef exp(coef) se(coef)     z      p
# days_drawn_processed                          0.20600   1.22875  0.09729 2.117 0.0342
# `Additive/Preservative`Streck DNA Stabilizer  2.77883  16.10017  1.37523 2.021 0.0433
# 
# Likelihood ratio test=26.08  on 2 df, p=2.176e-06
# n= 294, number of events= 150 
#    (200 observations deleted due to missingness)
# the signficant asssociation between Streck and hemolysis can be tested among those samples without lipedimia, compared with EDTA

fit.clr <- clogit(hemo_flag ~ days_drawn_processed + `Additive/Preservative`+ Specimen_Character + strata(BioSpm_ColIDScan_v1r0...6, BioPack_BoxID_v1r0),
+                   data = hemo_plasma.dup[which(hemo_plasma.dup$`Additive/Preservative`!="Lithium Heparin" ),])
```

The plots of these main factors (exposure) by the degree of the hemolysis

```{r}
#| echo: false
#| eval: true
#| include: false
#| warning: false

# [hide] 
ggplot(hemo_plasma,aes(x = Hemolyzed, y = Box_Temperature_arrival,fill=BioPack_BoxID_v1r0,color=BioPack_BoxID_v1r0)) +geom_point()

tmp <- melt(hemo_plasma[,c("Hemolyzed","anticoagulant","Box_Temperature_arrival","Box_Teperature_Lowest_transit","Temperature_changes_C","days_drawn_processed")], id.vars= c("Hemolyzed", "anticoagulant"))
  
  print(ggplot(tmp, aes(x=Hemolyzed,y=value,fill=Hemolyzed)) +geom_jitter(alpha=0.2) +geom_violin(alpha=0.25) + facet_grid(variable ~.) + scale_y_sqrt() + scale_fill_manual(values = c("lightblue","yellow","pink",  "red") )+
  theme(panel.background = element_blank(),
        legend.title = element_text(size=7),
        legend.position = "bottom",
        axis.line = element_line(linewidth=0.2),
        axis.text.x = element_text(hjust = 0.5,size = 8, face = "bold"),                             plot.title = element_text(hjust = 0.5,size = 12, face = "bold")))

print(ggplot(tmp[which(tmp$variable != "days_drawn_processed"),], aes(x=Hemolyzed,y=value, fill=Hemolyzed)) +geom_jitter(alpha=0.2) +geom_violin(alpha=0.50) + facet_grid(variable ~.) + scale_y_sqrt() + scale_fill_manual(values = c("lightblue","yellow","pink",  "red") )+
    theme(panel.background = element_blank(),
          legend.title = element_text(size=7),
          legend.position = "bottom",
          axis.line=element_line(linewidth=0.2),
          axis.text.x = element_text(hjust = 0.5,size = 8, face = "bold"),                             plot.title = element_text(hjust = 0.5,size = 12, face = "bold"))  )  
  
 print( ggplot(tmp[which(tmp$variable == "days_drawn_processed"),], aes(x=Hemolyzed,y=value, fill=Hemolyzed)) +geom_jitter(alpha=0.2) +geom_violin(alpha=0.75) + facet_grid(variable ~.) + scale_y_sqrt() + scale_fill_manual(values = c("lightblue","yellow","pink",  "red") )+
    theme(panel.background = element_blank(),
          legend.title = element_text(size=7),
          legend.position = c(0.75,0.5),
          axis.line=element_line(linewidth=0.2),
          axis.text.x = element_text(hjust = 0.5,size = 8, face = "bold"),                             plot.title = element_text(hjust = 0.5,size = 12, face = "bold")))

print(ggplot(tmp[which(tmp$variable == "days_drawn_processed"),], aes(x=Hemolyzed,y=value, fill=Hemolyzed, color=anticoagulant)) +geom_jitter(alpha=0.2) +geom_violin(alpha=0.75) + facet_grid(variable ~.) + scale_y_sqrt() + scale_fill_manual(values = c("lightblue","yellow","pink",  "red") )+
    theme(panel.background = element_blank(),
          legend.title = element_text(size=7),
          legend.position = "bottom",
          axis.line=element_line(linewidth=0.2),
          axis.text.x = element_text(hjust = 0.5,size = 8, face = "bold"),                             plot.title = element_text(hjust = 0.5,size = 12, face = "bold")))  
  
# ggplot(hemo_plasma, aes(x=Hemolyzed,y=anticoagulant, fill=Hemolyzed))+ geom_jitter(alpha=0.2) +geom_violin(alpha=0.75) + facet_grid(variable ~.) + scale_y_sqrt() + scale_fill_manual(values = c("lightblue","yellow","pink",  "red") )+
#     theme(panel.background = element_blank(),
#           legend.title = element_text(size=7),
#           legend.position = c(0.75,0.5),
#           axis.line=element_line(linewidth=0.2),
#           axis.text.x = element_text(hjust = 0.5,size = 8, face = "bold"),                             plot.title = element_text(hjust = 0.5,size = 12, face = "bold"))
# 

tmp <- melt(hemo_plasma[,c("Hemolyzed","anticoagulant","Box_Temperature_arrival","Box_Teperature_Lowest_transit","Temperature_changes_C","days_drawn_processed")], id.vars= c("Hemolyzed", "anticoagulant"))

tmp2 <- hemo_plasma %>% dplyr::select(`Additive/Preservative`, Hemolyzed) %>%  group_by(`Additive/Preservative`,Hemolyzed) %>% 
  dplyr::summarise(n = dplyr::n(), .groups = "drop") %>% 
  mutate(Hemolyzed = factor(Hemolyzed, levels= c("not hem (1)","slight hemo (2-3)","mod hem(4-5)", "severe hemo (6-7)" )))    

#legend_title = "Hemolysis"
print(ggplot(tmp2,aes(x = `Additive/Preservative`, y =n, fill=factor(Hemolyzed,levels=c( "severe hemo (6-7)","mod hem(4-5)","slight hemo (2-3)", "not hem (1)"))),size = n,color="black",vjust = -0.20,position = position_dodge(width=-0.6),angle=-35) + geom_jitter() +
    geom_bar(position="stack",stat="identity",na.rm=TRUE,color="grey")+ 
  scale_fill_manual("Hemolysis",values = c( "red","pink","yellow","lightblue" ) )+
  scale_y_continuous(name="Individuals, N")+
  #scale_x_discrete(limits=c("Initial Srv+Blood","Blood.Only","Survey.Only","Verified.noActivities","Expected.toVerified"),drop=FALSE)+
 # geom_text(aes(y=label.count, label= Expected_Verified_n),color="black",vjust=1.0,size=3.0) + labs(x = "", y = "# Participants") +
  stat_summary(fun.y = sum, aes(label = ..y.., group = `Additive/Preservative`), geom = "text",hjust = 1.5,vjust=-0.5,size=3.5) +
  labs( title="Days from Drawn to Processing of Blood vs Hemolysis  \nby Anticoagulant")+
  theme(panel.background = element_blank(),
        legend.title = element_text(size=7),
        legend.position = "bottom",
        axis.line = element_line(size=0.2),
        axis.text.x = element_text(hjust = 0.5,size = 8, face = "bold"),
        plot.title = element_text(hjust = 0.5,size = 12, face = "bold")))

print(ggplot(tmp[which(tmp$variable == "days_drawn_processed"),], aes(x=Hemolyzed,y=value, fill=Hemolyzed, color=`anticoagulant`)) +geom_jitter(alpha=0.2) +geom_violin(alpha=0.5) + facet_grid(variable ~.) + scale_y_sqrt() + scale_fill_manual(values = c("blue","yellow","green",  "red") )+
    theme(panel.background = element_blank(),
          legend.title = element_text(size=7),
          legend.position = "bottom",
          axis.line=element_line(linewidth=0.2),
          axis.text.x = element_text(hjust = 0.5,size = 8, face = "bold"),                             plot.title = element_text(hjust = 0.5,size = 12, face = "bold")))

ggplot(tmp[which(tmp$variable != "days_drawn_processed"),], aes(x=Hemolyzed,y=value, fill=Hemolyzed, color=`anticoagulant`)) +geom_jitter(alpha=0.2) +geom_violin(alpha=0.5) + facet_grid(variable ~.) + scale_y_sqrt() + scale_fill_manual(values = c("blue","yellow","green",  "red") )+
    theme(panel.background = element_blank(),
          legend.title = element_text(size=7),
          legend.position = "bottom",
          axis.line=element_line(linewidth=0.2),
          axis.text.x = element_text(hjust = 0.5,size = 8, face = "bold"),                             plot.title = element_text(hjust = 0.5,size = 12, face = "bold"))
```

```{r}

#| echo: false
#| include: false
# [hide] 

# ggplot(hemo_plasma,aes(x = Hemolyzed, y = Box_Temperature_arrival,fill=BioPack_BoxID_v1r0,color=BioPack_BoxID_v1r0)) +geom_point()
# 
# tmp <- melt(hemo_plasma[,c("Hemolyzed","anticoagulant","Box_Temperature_arrival","Box_Teperature_Lowest_transit","Temperature_changes_C","days_drawn_processed")], id.vars= c("Hemolyzed", "anticoagulant"))
#   
#   ggplot(tmp, aes(x=Hemolyzed,y=value,fill=Hemolyzed)) +geom_jitter(alpha=0.2) +geom_violin(alpha=0.25) + facet_grid(variable ~.) + scale_y_sqrt() + scale_fill_manual(values = c("lightblue","yellow","pink",  "red") )+
#   theme(panel.background = element_blank(),
#         legend.title = element_text(size=7),
#         legend.position = c(0.75,0.9),
#         axis.line = element_line(linewidth=0.2),
#         axis.text.x = element_text(hjust = 0.5,size = 8, face = "bold"),                             plot.title = element_text(hjust = 0.5,size = 12, face = "bold")) 
# 
#  ggplot(tmp[which(tmp$variable != "days_drawn_processed"),], aes(x=Hemolyzed,y=value, fill=Hemolyzed)) +geom_jitter(alpha=0.2) +geom_violin(alpha=0.50) + facet_grid(variable ~.) + scale_y_sqrt() + scale_fill_manual(values = c("lightblue","yellow","pink",  "red") )+
#     theme(panel.background = element_blank(),
#           legend.title = element_text(size=7),
#           legend.position = "bottom",
#           axis.line=element_line(linewidth=0.2),
#           axis.text.x = element_text(hjust = 0.5,size = 8, face = "bold"),                             plot.title = element_text(hjust = 0.5,size = 12, face = "bold"))   
#   
#   ggplot(tmp[which(tmp$variable == "days_drawn_processed"),], aes(x=Hemolyzed,y=value, fill=Hemolyzed)) +geom_jitter(alpha=0.2) +geom_violin(alpha=0.75) + facet_grid(variable ~.) + scale_y_sqrt() + scale_fill_manual(values = c("lightblue","yellow","pink",  "red") )+
#     theme(panel.background = element_blank(),
#           legend.title = element_text(size=7),
#           legend.position = c(0.75,0.5),
#           axis.line=element_line(linewidth=0.2),
#           axis.text.x = element_text(hjust = 0.5,size = 8, face = "bold"),                             plot.title = element_text(hjust = 0.5,size = 12, face = "bold"))
# 
# ggplot(tmp[which(tmp$variable == "days_drawn_processed"),], aes(x=Hemolyzed,y=value, fill=Hemolyzed, color=anticoagulant)) +geom_jitter(alpha=0.2) +geom_violin(alpha=0.75) + facet_grid(variable ~.) + scale_y_sqrt() + scale_fill_manual(values = c("lightblue","yellow","pink",  "red") )+
#     theme(panel.background = element_blank(),
#           legend.title = element_text(size=7),
#           legend.position = c(0.75,0.5),
#           axis.line=element_line(linewidth=0.2),
#           axis.text.x = element_text(hjust = 0.5,size = 8, face = "bold"),                             plot.title = element_text(hjust = 0.5,size = 12, face = "bold"))  
#   
# ggplot(hemo_plasma, aes(x=Hemolyzed,y=anticoagulant, fill=Hemolyzed)) +geom_jitter(alpha=0.2) +geom_violin(alpha=0.75) + facet_grid(variable ~.) + scale_y_sqrt() + scale_fill_manual(values = c("lightblue","yellow","pink",  "red") )+
#     theme(panel.background = element_blank(),
#           legend.title = element_text(size=7),
#           legend.position = c(0.75,0.5),
#           axis.line=element_line(linewidth=0.2),
#           axis.text.x = element_text(hjust = 0.5,size = 8, face = "bold"),                             plot.title = element_text(hjust = 0.5,size = 12, face = "bold"))
# 
# 
# tmp <- melt(hemo_plasma[,c("Hemolyzed","anticoagulant","Box_Temperature_arrival","Box_Teperature_Lowest_transit","Temperature_changes_C","days_drawn_processed")], id.vars= c("Hemolyzed", "anticoagulant"))
# 
# tmp2 <- hemo_plasma %>% dplyr::select(`Additive/Preservative`, Hemolyzed) %>%  group_by(`Additive/Preservative`,Hemolyzed) %>% 
#   dplyr::summarise(n = dplyr::n(), .groups = "drop") %>% 
#   mutate(Hemolyzed = factor(Hemolyzed, levels= c("not hem (1)","slight hemo (2-3)","mod hem(4-5)", "severe hemo (6-7)" )))    
# 
# legend_title = "Hemolysis"
# ggplot(tmp2,aes(x = `Additive/Preservative`, y =n, fill=factor(Hemolyzed,levels=c( "severe hemo (6-7)","mod hem(4-5)","slight hemo (2-3)", "not hem (1)"))),size = n,color="black",vjust = -0.20,position = position_dodge(width=-0.6),angle=-35) + geom_jitter() +
#     geom_bar(position="stack",stat="identity",na.rm=TRUE,color="grey")+ 
#   scale_fill_manual("Hemolysis",values = c( "red","pink","yellow","lightblue" ) )+
#   scale_y_continuous(name="Individuals, N")+
#   #scale_x_discrete(limits=c("Initial Srv+Blood","Blood.Only","Survey.Only","Verified.noActivities","Expected.toVerified"),drop=FALSE)+
#  # geom_text(aes(y=label.count, label= Expected_Verified_n),color="black",vjust=1.0,size=3.0) + labs(x = "", y = "# Participants") +
#   stat_summary(fun.y = sum, aes(label = ..y.., group = `Additive/Preservative`), geom = "text",hjust = 1.5,vjust=-0.5,size=3.5) +
#   labs( title="Days from Drawn to Processing of Blood vs Hemolysis  \nby Anticoagulant")+
#   theme(panel.background = element_blank(),
#         legend.title = element_text(size=7),
#         legend.position = "bottom",
#         axis.line = element_line(size=0.2),
#         axis.text.x = element_text(hjust = 0.5,size = 8, face = "bold"),
#         plot.title = element_text(hjust = 0.5,size = 12, face = "bold"))
# 
# ggplot(tmp[which(tmp$variable == "days_drawn_processed"),], aes(x=Hemolyzed,y=value, fill=Hemolyzed, color=`Additive/Preservative`)) +geom_jitter(alpha=0.2) +geom_violin(alpha=0.5) + facet_grid(variable ~.) + scale_y_sqrt() + scale_fill_manual(values = c("blue","yellow","green",  "red") )+
#     theme(panel.background = element_blank(),
#           legend.title = element_text(size=7),
#           legend.position = "bottom",
#           axis.line=element_line(linewidth=0.2),
#           axis.text.x = element_text(hjust = 0.5,size = 8, face = "bold"),                             plot.title = element_text(hjust = 0.5,size = 12, face = "bold"))
  
  #ggplot(hemo_plasma,aes(x = BioPack_BoxID_v1r0, y = Box_Temperature_arrival,fill=Hemolyzed),size = 3,color="black",vjust = -0.20,position = position_dodge(width=-0.6),angle=-35) + 
#  geom_bar(position="stack",stat="identity",na.rm=TRUE,color="grey")+ 
   
#   scale_fill_manual(values = c("white","lightblue","yellow",  "red","pink") )
# ggplot(hemo_plasma,aes(x = BioPack_BoxID_v1r0, y = Box_Temperature_arrival,fill=Hemolyzed),size = 3,color="black",vjust = -0.20,position = position_dodge(width=-0.6),angle=-35) + 
#   geom_bar(position="stack",stat="identity",na.rm=TRUE,color="grey")+ 
#   
#   scale_fill_manual(values = c("white","lightblue","yellow",  "red","pink") )+
#   scale_y_continuous(name="Individuals, N", breaks=c(100,500,1000,1500,2000,2500,3000) )+
#   #scale_x_discrete(limits=c("Initial Srv+Blood","Blood.Only","Survey.Only","Verified.noActivities","Expected.toVerified"),drop=FALSE)+
#   geom_text(aes(y=label.count, label= Expected_Verified_n),color="black",vjust=1.0,size=3.0) + labs(x = "", y = "# Participants") + 
#   stat_summary(fun.y = sum, aes(label = ..y.., group = Site), geom = "text",hjust = 1.5,vjust=-0.5,size=3.5) +
#   labs( title=str_wrap(paste("Total Expected Recruits vs Actual Verified Recruitments vs. \nNumbers of Blood Collections till",currentDate, sep=" "),  60),
#         x = "Recruitment Sites")+
#   theme(panel.background = element_blank(),
#         legend.title = element_text(size=7),
#         legend.position = c(0.75,0.9),
#         axis.line = element_line(size=0.2),
#         axis.text.x = element_text(hjust = 0.5,size = 8, face = "bold"),                                                            
#         plot.title = element_text(hjust = 0.5,size = 12, face = "bold")) 
```

Here is the tables for the file "HP Streck tube pilot analysis plan for Jing Feb 2024_updated.docx" with more comments from Stephanie after the meeting on Wednesday, Feb. 7, 2024.

1\. Cross tab frequency of the categorical hemolysis outcome by tube type.  For tube type you can use the additive/preservative in column T, to add the "total across rows"

```{r}
#| hide:
#| echo: false
#| eval: true
#| code-fold: true
#| code-summary: "Show the code"

hemo_additive <- hemolysis %>% 
  dplyr::select(Hemolyzed,hemolysis$anticoagulant) %>%
  tbl_cross(col = Hemolyzed,
            row = anticoagulant,
            label = list(Hemolyzed~"Hemolysis outcomes",
                         anticoagulant ~"Anticoagulants/Preservative" ),
            digits=c(0,2),
            percent = c("row"),
            missing = "ifany",
            margin_text = "Total Blood Samples",
            missing_text = "(Missing)") %>%
            bold_labels() %>%
           #italicize_levels() %>% 
            modify_header() 

hemo_additive2 <- hemolysis %>% 
  dplyr::select(Hemolyzed,anticoagulant) %>%
  tbl_cross(col = Hemolyzed,
            row = anticoagulant,
            label = list(Hemolyzed~"Hemolysis outcomes",
                         anticoagulant ~"Anticoagulants/Preservative" ),
            digits=c(0,2),
            percent = c("row"),
            margin_text = "Total Blood Samples",
            missing = "no") %>%
            bold_labels() %>%
           #italicize_levels() %>% 
            modify_header() 

hemo_additive1 <- hemolysis %>% 
  dplyr::select(hemo_class,anticoagulant) %>%
  tbl_cross(col = hemo_class,
            row = anticoagulant,
            label = list(hemo_class~"Hemolysis outcomes",
                         anticoagulant ~"Anticoagulants/Preservative" ),
            digits=c(0,2),
            percent = c("row"),
            missing = "ifany",
            margin_text = "Total Blood Samples",
            missing_text = "(Missing)") %>%
            bold_labels() %>%
           #italicize_levels() %>% 
            modify_header(stat_1 = "Not Hemolyzed (1)", 
                          stat_2 = "Slighted Hemolyzed (2-3)" ,
                          stat_3 = "Moderate (4-5)/Servere Hemolyzed (6-7)",
                          stat_4 = "Uknown/Missing")
                          
                          
                          
                          
```

## 3. Examine the percent of hemolysis (any hemolysis yes/no and moderate & severe yes/no) of the Streck DNA Stabilizer tube by phlebotomist (initials in column Y)

a.  Row percents, total number will be row denominator;

b.  to combine the initials: CG and CSG, All three of these are one person (OJ, OJS, OS);

```{r}
hemolysis <- hemolysis %>% 
  mutate(Phlebotomist = ifelse(toupper(BioCol_PhlebInitials_v1r0) %in% c("CG","CSG"),"CG/CSG", ifelse(toupper(BioCol_PhlebInitials_v1r0) %in% c("OJ","OJS","OS"), "OJ/OJS/OS",toupper(BioCol_PhlebInitials_v1r0) )))
table(hemolysis$Phlebotomist,hemolysis$anticoagulant)
  #          
  #           EDTA = K2 Lithium Heparin SST Streck DNA Stabilizer
  # AM              104              67 209                   104
  # AN               14               9  28                    14
  # CG/CSG           71              32 143                    71
  # OJ/OJS/OS       106              76 216                   105
  # WC               59              31 122                    59


hemo_phlebotomist <- hemolysis %>% 
  select(hemo_flag,Phlebotomist) %>%
  tbl_cross(col = hemo_flag,
            row = Phlebotomist,
            label = list(hemo_flag~"Any hemolysis",
                         Phlebotomist ~"Phlebotomist" ),
            digits=c(0,2),
            percent = c("row"),
            missing = "ifany",
            margin_text = "Total Blood",
            missing_text = "(Missing)") %>%
            bold_labels() %>%
           #italicize_levels() %>% 
           modify_header() 

hemo_phlebotomist1 <- hemo_plasma %>% 
    select(hemo_flag,Phlebotomist) %>%
    tbl_cross(col = hemo_flag,
              row = Phlebotomist,
              label = list(hemo_flag~"Any hemolysis",
                           Phlebotomist ~"Phlebotomist" ),
              digits=c(0,2),
              percent = c("col"),
              missing = "ifany",
              margin_text = "Total Plasma Samples",
              missing_text = "(Missing)") %>%
    bold_labels() %>%
    #italicize_levels() %>% 
    modify_header() 

hemo_phlebotomist2 <- filter(hemolysis, `Additive/Preservative` == "Streck DNA Stabilizer") %>% mutate(Phlebotomist = ifelse(toupper(BioCol_PhlebInitials_v1r0) %in% c("CG","CSG"),"CG/CSG", ifelse(toupper(BioCol_PhlebInitials_v1r0) %in% c("OJ","OJS","OS"), "OJ/OJS/OS",toupper(BioCol_PhlebInitials_v1r0) ))) %>% 
    select(hemo_flag,Phlebotomist) %>%
    tbl_cross(col = hemo_flag,
              row = Phlebotomist,
              label = list(hemo_flag~"Any hemolysis",
                           Phlebotomist ~"Phlebotomist" ),
              digits=c(0,2),
              percent = c("col"),
              missing = "no",
              margin_text = "Total Blood Samples") %>%
    bold_labels() %>%
    #italicize_levels() %>% 
    modify_header(stat_0 ~"Total Streck Tubes",
                  stat_1 ~"Not Hemolyzed (1)", 
                  stat_2 = "Any Hemolyzed (2-7)" ) 

hemo_phlebotomist3 <- filter(hemolysis, `Additive/Preservative` == "Streck DNA Stabilizer") %>% mutate(Phlebotomist = ifelse(toupper(BioCol_PhlebInitials_v1r0) %in% c("CG","CSG"),"CG/CSG", ifelse(toupper(BioCol_PhlebInitials_v1r0) %in% c("OJ","OJS","OS"), "OJ/OJS/OS",toupper(BioCol_PhlebInitials_v1r0) ))) %>% 
    select(hemo_class,Phlebotomist) %>%
    tbl_cross(col = hemo_class,
              row = Phlebotomist,
              label = list(hemo_class~"Moderate /Servere hemolysis (2-7)",
                           Phlebotomist ~"Phlebotomist" ),
              digits=c(0,2),
              percent = c("col"),
              missing = "no",
              margin_text = "Total Blood Samples") %>%
    bold_labels() %>%
    #italicize_levels() %>% 
    modify_header(stat_0 ~"Total Streck Tubes",
                  stat_1 ~"Not Hemolyzed (1)", 
                  stat_2 = "Slightly Hemolyzed (2-3)",
                  stat_3 = "Moderate (4-5)/Servere Hemolyzed (6-7)" ) 
```

4\. Examine the percent of hemolysis (any hemolysis yes/no and moderate & severe yes/no) of the Streck DNA Stabilizer tube by clinical vs research collection (clinical = had data in column G; research = has data in column H)

```{r}
hemo_Setting <- filter(hemolysis, `Additive/Preservative` == "Streck DNA Stabilizer") %>% 
    select(hemo_flag,BioSpm_Setting_v1r0) %>%
    tbl_cross(col = hemo_flag,
              row = BioSpm_Setting_v1r0,
              label = list(hemo_flag~"Any hemolysis (2-7)",
                           BioSpm_Setting_v1r0 ~"Setting" ),
              digits=c(0,2),
              percent = c("row"),
              missing = "ifany",
              margin_text = "Total Blood Streck Samples",
              missing_text = "Missing") %>%
    bold_labels() %>%
    #italicize_levels() %>% 
    modify_header(stat_0 ~"Total Streck Tubes",
                  stat_1 ~"Not Hemolyzed (1)", 
                  stat_2 = "Any Hemolyzed (2-7)") 

hemo_Setting1 <- filter(hemolysis, `Additive/Preservative` == "Streck DNA Stabilizer") %>% 
    select(hemo_class,BioSpm_Setting_v1r0) %>%
    tbl_cross(col = hemo_class,
              row = BioSpm_Setting_v1r0,
              label = list(hemo_class~"Moderate /Servere hemolysis (4-7)",
                           BioSpm_Setting_v1r0 ~"Setting" ),
              digits=c(0,2),
              percent = c("row"),
              missing = "ifany",
              margin_text = "Total Blood Streck Samples",
              missing_text = "Missing") %>%
    bold_labels() %>%
    #italicize_levels() %>% 
    modify_header(stat_0 ~"Total Streck Tubes",
                  stat_1 ~"Not Hemolyzed (1)", 
                  stat_2 = "Slightly Hemolyzed (2-3)",
                  stat_3 = "Moderate (4-5)/Servere Hemolyzed (6-7)" ) 
```

5.Examine the percent of hemolysis (any hemolysis yes/no and moderate & severe yes/no) of the Streck DNA Stabilizer tube by needle-to-receipt time in days

(Column Q = Needle to receipt time in days)

```{r}
hemo_NeedleRecpt <- filter(hemolysis, `Additive/Preservative` == "Streck DNA Stabilizer") %>%   dplyr::select(hemo_flag,days_received_drawn) %>%
  tbl_cross(col = hemo_flag,
            row = days_received_drawn,
            label = list(hemo_flag~"Any Hemolysis",
                         days_received_drawn ~"Days from Blood Drawn to Received" ),
            digits=c(0,2),
            percent = c("row"),
            missing = "ifany",
            margin_text = "Total Plasma",
            missing_text = "(Missing)") %>%
            bold_labels() %>%
           #italicize_levels() %>% 
           modify_header() 

hemo_NeedleRecpt1 <- filter(hemolysis, `Additive/Preservative` == "Streck DNA Stabilizer") %>%   dplyr::select(hemo_class,days_received_drawn) %>%
  tbl_cross(col = hemo_class,
            row = days_received_drawn,
            label = list(hemo_class~"mod or severe hemolysis",
                         days_received_drawn ~"Days from Blood Drawn to Received" ),
            digits=c(0,2),
            percent = c("row"),
            missing = "ifany",
            margin_text = "Total Plasma",
            missing_text = "(Missing)") %>%
            bold_labels() %>%
           #italicize_levels() %>% 
           modify_header() 
```

6.Examine the percent of hemolysis (any hemolysis yes/no and moderate & severe yes/no) of the Streck DNA Stabilizer[\[SO1\]](#_msocom_1)  tube by needle-to-processed time in days

(Column R = Needle to processed time in days)

 [\[SO1\]](#_msoanchor_1)For Streck tubes only and fill in the table

```{r}
hemo_NeedleProcess <- filter(hemolysis, `Additive/Preservative` == "Streck DNA Stabilizer") %>%   dplyr::select(hemo_flag,days_drawn_process_cat) %>%
  tbl_cross(col = hemo_flag,
            row = days_drawn_process_cat,
            label = list(hemo_flag~"Any Hemolysis",
                         days_drawn_process_cat ~"Days from Blood Drawn to Processed" ),
            digits=c(0,2),
            percent = c("row"),
            missing = "ifany",
            margin_text = "Total Streck Tubes",
            missing_text = "(Missing)") %>%
            bold_labels() %>%
           #italicize_levels() %>% 
           modify_header() 

hemo__NeedleProcess1 <- filter(hemolysis, `Additive/Preservative` == "Streck DNA Stabilizer") %>%   dplyr::select(hemo_class,days_drawn_process_cat) %>%
  tbl_cross(col = hemo_class,
            row = days_drawn_process_cat,
            label = list(hemo_class~"mod or severe hemolysis",
                         days_drawn_process_cat ~"Days from Blood Drawn to Processed" ),
            digits=c(0,2),
            percent = c("row"),
            missing = "ifany",
            margin_text = "Total Streck Tubes",
            missing_text = "(Missing)") %>%
            bold_labels() %>%
           #italicize_levels() %>% 
           modify_header() 

hemo_lipemic <- filter(hemolysis, `Additive/Preservative` == "Streck DNA Stabilizer") %>% mutate(Specimen_Character=ifelse(is.na(`Specimen Character`), "not mentioned",`Specimen Character`)) %>%   dplyr::select(hemo_class,Specimen_Character) %>%
  tbl_cross(col = hemo_class,
            row = Specimen_Character,
            label = list(hemo_class~"mod or severe hemolysis",
                         Specimen_Character ~"Sample Characters" ),
            digits=c(0,2),
            percent = c("row"),
            missing = "ifany",
            margin_text = "Total Streck Tubes",
            missing_text = "(Missing)") %>%
            bold_labels() %>%
           #italicize_levels() %>% 
           modify_header() %>%
            modify_header(stat_0 ~"Total Streck Tubes",
                  stat_1 ~"Not Hemolyzed (1)", 
                  stat_2 = "Slightly Hemolyzed (2-3)",
                  stat_3 = "Moderate (4-5)/Servere Hemolyzed (4-7)" ) 


tubes_lipemic0 <- hemolysis %>% mutate(Specimen_Character=ifelse(is.na(`Specimen Character`), "not mentioned",`Specimen Character`)) %>%   dplyr::select(anticoagulant,Specimen_Character) %>%
    tbl_cross(col = anticoagulant,
              row = Specimen_Character,
              label = list(anticoagulant~"Additive /Preservative",
                           Specimen_Character ~"Sample Characters" ),
              digits=c(0,2),
              percent = c("row"),
              missing = "ifany",
              margin_text = "Total Streck Tubes",
              missing_text = "(Missing)") %>%
    bold_labels() %>%
    #italicize_levels() %>% 
    modify_header() %>%
    modify_header(stat_0 ~"Total Blood Tubes",
                  stat_1 ~"EDTA = K2", 
                  stat_2 = "Lithium Heparin",
                  stat_3 = "Streck DNA Stabilizer", 
                  stat_4 = "SST") 

nolip_strk <- filter(hemolysis, is.na(`Specimen Character`)) 
                     
                     
```

8.Plot all categories of hemolysis (all categories) by lowest temperature (column Z ” Box Lowest Temp during Transit”) with temperature across the X axis and hemolysis categories on the Y axis (not hemolyzed at the bottom and then slight, then moderate, then severe going up the y axis) and plot each point for the Streck DNA Stabilizer tubes only.[\[SO1\]](#_msocom_1) 

 [\[SO1\]](#_msoanchor_1)Redo with Streck tube only and drop the temp change one

```{r}
tmp2 <- melt(hemolysis[which(hemolysis$`Additive/Preservative` == "Streck DNA Stabilizer"),c("Hemolyzed","anticoagulant","Box_Temperature_arrival","Box_Teperature_Lowest_transit","Temperature_changes_C","days_drawn_processed")], id.vars= c("Hemolyzed", "anticoagulant"))

print(ggplot(tmp2[which(tmp2$variable != "days_drawn_processed"),], aes(x=Hemolyzed,y=value, fill=Hemolyzed)) +geom_jitter(alpha=0.2) +geom_violin(alpha=0.50) + facet_grid(variable ~.) + scale_y_sqrt() + scale_fill_manual(values = c("lightblue","yellow","pink",  "red") )+
    theme(panel.background = element_blank(),
          legend.title = element_text(size=7),
          legend.position = "bottom",
          axis.line=element_line(linewidth=0.2),
          axis.text.x = element_text(hjust = 0.5,size = 8, face = "bold"),                             plot.title = element_text(hjust = 0.5,size = 12, face = "bold"))  ) 
```

```{r}
hemo_plasma.dup <- filter(hemo_plasma, BioSpm_ColIDScan_v1r0...6 %in% collectID.nodup, grepl("Streck|EDTA",`Additive/Preservative` )) 
table(hemo_plasma.dup$Hemolyzed,hemo_plasma.dup$`Additive/Preservative`)


plasma_dup_check1 <- hemo_plasma.dup %>% select(Connect_ID, BioSpm_ColIDScan_v1r0...6, anticoagulant,Hemolyzed) %>% group_by(Connect_ID, BioSpm_ColIDScan_v1r0...6 ) %>% pivot_wider(names_from= anticoagulant, values_from=Hemolyzed, values_fill=NA)

plasma_dup_check1 <- plasma_dup_check1 %>% 
  mutate( hemolyzed_both = case_when(`EDTA = K2` == `Streck DNA Stabilizer` ~ paste0("both= ", `EDTA = K2`) ,
                                    "EDTA = K2" != "Streck DNA Stabilizer" ~ paste(`Streck DNA Stabilizer`,`EDTA = K2`,sep=" vs "))) 
  plasma_dup_pairs <- plasma_dup_check1 %>% select(hemolyzed_both) %>% tbl_summary(
    statistic = list(all_categorical() ~ "{n} / {N} ({p}%)")) %>%
    #add_p(pvalue_fun = ~ style_pvalue(.x, digits = 2)) %>%
    #add_overall() %>%
    add_n() %>%
    modify_header(label ~ "**Variable**") %>%
    #modify_spanning_header(c("stat_1", "stat_2") ~ "**Hemolyzed Status**") %>%
    modify_footnote(
        all_stat_cols() ~ "EDTA vs Streck on Hemolysis"
    ) %>%
    modify_caption("**Table 1. Blood Plasma Collection on Hemolysis in pairs**") %>%
    bold_labels() %>%
    as_kable_extra(escape = FALSE, addtl_fmt = TRUE)
  
  plasma_dup_check2 <- hemo_plasma.dup %>% select(Connect_ID, BioSpm_ColIDScan_v1r0...6, anticoagulant,Specimen_Character) %>% group_by(Connect_ID, BioSpm_ColIDScan_v1r0...6 ) %>% pivot_wider(names_from= anticoagulant, values_from=Specimen_Character, values_fill=NA) %>% mutate( lipedmia_both = case_when(`EDTA = K2` == `Streck DNA Stabilizer` ~ paste0("both= ", `EDTA = K2`) ,
                                    "EDTA = K2" != "Streck DNA Stabilizer" ~ paste(`Streck DNA Stabilizer`,`EDTA = K2`,sep=" vs "))) 
  
  

```

Feb. 27, 2024, Stephanie has just sent me another data set (<https://nih.app.box.com/file/1456100207253?s=or6sg8xxj0jrohn0ia8z5p6760ti82gh>) [which](https://nih.app.box.com/file/1456100207253?s=or6sg8xxj0jrohn0ia8z5p6760ti82gh) to check "

([https://app.box.com/s/or6sg8xxj0jrohn0ia8z5p6760ti82gh](https://gcc02.safelinks.protection.outlook.com/?url=https%3A%2F%2Fapp.box.com%2Fs%2For6sg8xxj0jrohn0ia8z5p6760ti82gh&data=05%7C02%7Cjing.wu2%40nih.gov%7Cca46c2b005884d4f0efa08dc37e33484%7C14b77578977342d58507251ca2dc2b06%7C0%7C0%7C638446696170775202%7CUnknown%7CTWFpbGZsb3d8eyJWIjoiMC4wLjAwMDAiLCJQIjoiV2luMzIiLCJBTiI6Ik1haWwiLCJXVCI6Mn0%3D%7C0%7C%7C%7C&sdata=es8Z1%2FgoB93ndi9KKeDoSXm9kK9LiraWa8xjgt3G0Vk%3D&reserved=0 "https://gcc02.safelinks.protection.outlook.com/?url=https%3A%2F%2Fapp.box.com%2Fs%2For6sg8xxj0jrohn0ia8z5p6760ti82gh&data=05%7C02%7Cjing.wu2%40nih.gov%7Cca46c2b005884d4f0efa08dc37e33484%7C14b77578977342d58507251ca2dc2b06%7C0%7C0%7C638446696170775202%7CUnknown%7CTWFpbGZsb3d8eyJWIjoiMC4wLjAwMDAiLCJQIjoiV2luMzIiLCJBTiI6Ik1haWwiLCJXVCI6Mn0%3D%7C0%7C%7C%7C&sdata=es8Z1%2FgoB93ndi9KKeDoSXm9kK9LiraWa8xjgt3G0Vk%3D&reserved=0")  (using the first tab in the spreadsheet called “first aliquot”).

 

I have selected 40 samples from the file that we are going to send out for some assays.  I selected all the samples that are frozen (n=11), then the rest were selected based on the needle-to-frozen time, trying to get a distribution of that.  We hope we also end up with a variety of hemolysis.  

 

The last column shows which ones have been selected:

1=selected (not frozen); 2= selected (frozen); 3=not selected

 

Could you use the data in the file to fill in the attached tables?  I want to make sure that the samples we selected are representative of all of the samples in the file.  Note that the first 28 that have a missing or negative needle-to-frozen time should be remove from the analysis.

 

Use the column: “needle to frozen SJW calculation” for the calculations in the second table."

```{r}

box_setwd(dir_id =244206033569)
batch2 <- box_read(file_id=1456100207253) 

batch2 <- batch2 %>% mutate(Selected = case_when(selected==1 ~'selected (not frozen)',
                                                  selected==2 ~ 'selected (frozen)',
                                                  selected==3 ~ 'not selected'),
                             Selected = factor(Selected, levels= c("selected (not frozen)","selected (frozen)","not selected")),
                             Specimen_Character=ifelse(is.na(`Specimen Character`), "not mentioned",`Specimen Character`),
                             Hemolyzed = factor(Hemolyzed, levels= c("not hem (1)","slight hemo (2-3)","mod hem(4-5)", "severe hemo (6-7)" ))) 

batch2$days_drawn_processed =difftime(batch2$"Date Processed", batch2$"Date Drawn",units="days")
hemo_select <- filter(batch2, `needle to frozen SJW calculation` >=0) %>% 
  select(Hemolyzed,Selected) %>%
  tbl_cross(col = Hemolyzed,
            row = Selected,
            label = list(Hemolyzed~"Hemolyzed status",
                         Selected ~"Selected Settings" ),
            digits=c(0,2),
            percent = c("col"),
            missing = "ifany",
            margin_text = "Total Plasma",
            missing_text = "(Missing)") %>%
            bold_labels() %>%
           #italicize_levels() %>% 
           modify_header() 

select1 <- filter(batch2, `needle to frozen SJW calculation` >=0) %>% select(Selected,`needle to frozen SJW calculation`) %>% 
  group_by(Selected) %>% 
  dplyr::summarize(`Number Selected`=n(),
                   min = min(`needle to frozen SJW calculation`),
                   pct10 = quantile(`needle to frozen SJW calculation`, 0.10),
                   q1 = quantile(`needle to frozen SJW calculation`, 0.25),
                   median = median(`needle to frozen SJW calculation`),
                   mean = mean(`needle to frozen SJW calculation`),sd=sd(`needle to frozen SJW calculation`),
                   q3 = quantile(`needle to frozen SJW calculation`, 0.75),
                   pct90 = quantile(`needle to frozen SJW calculation`, 0.90),
                   max = max(`needle to frozen SJW calculation`))

select0 <- filter(batch2, `needle to frozen SJW calculation` >=0) %>% select(Selected,`needle to frozen SJW calculation`) %>% 
  dplyr::summarize(`Number Selected`=n(),
                   min = min(`needle to frozen SJW calculation`),
                   pct10 = quantile(`needle to frozen SJW calculation`, 0.10),
                   q1 = quantile(`needle to frozen SJW calculation`, 0.25),
                   median = median(`needle to frozen SJW calculation`),
                   mean = mean(`needle to frozen SJW calculation`),sd=sd(`needle to frozen SJW calculation`),
                   q3 = quantile(`needle to frozen SJW calculation`, 0.75),
                   pct90 = quantile(`needle to frozen SJW calculation`, 0.90),
                   max = max(`needle to frozen SJW calculation`))

```
